RadLib: a radiative heat transfer model library for CFD

### 2020-12-21 manuscript/manuscript.tex
proofreading edits to rcslw section

In the RCSLW model for a given problem, a collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$. The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position (and corresponding thermodynamic state $\BS{\phi}$) can then be found by inversion: $C_j = C(F_j,\BS{\phi},T_r)$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$. $\kappa_j$ is then computed as $\kappa_j=C_jN$, and $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature, not $T_r$.

>>>>

In the RCSLW model for a given problem, a collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$; these apply to all spatial positions. The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position (and corresponding thermodynamic state $\BS{\phi}$) can then be found by inversion: $C_j = C(F_j,\BS{\phi},T_r)$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$. $\kappa_j$ is then computed as $\kappa_j=C_jN$, and $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature, not $T_r$. The system average temperature may be used for $T_r$, as done in \cite{Solovjov_2001}, and in the examples below.
